Flowchart of Current Algorithm

### 2010-03-28 docs/flowchart/flowchart.tex
add the graphical flowcharts from the multilevel paper

>>>>

%-----------------------------------------------------------------------------
% graphical flowcharts
%-----------------------------------------------------------------------------
\begin{figure}[tb]
\centering
\includegraphics[scale=0.6]{flowchart}
\caption{\label{Fig:flowchart} A flowchart of the algorithm.  The
  thermodynamic state variables, base state variables, and local velocity are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  The predictor-corrector steps are
  outlined by the dotted box.  The blue text indicates state
  variables that are the same in {\bf Step 6} as they are in
  {\bf Step 2}, i.e., they are unchanged by the predictor steps.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                               
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                               
\begin{figure}[tb]                                                              
\centering
\includegraphics[scale=0.6]{flowchart_4_8}
\caption{\label{Fig:flowchart48}
A flowchart for {\bf Steps 4} and {\bf 8}.  The thermodynamic state variables
and base state variables are indicated in each step.  Red text indicates that q\
uantity
was updated during that step.  Note, for {\bf Step 4}, the updated
quantities should also have a $\star$ superscript, e.g., {\bf Step 8I} defines
$T^{(2)}$ while {\bf Step 4I} defines $T^{(2),\star}$ .}
\end{figure}
